First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-07-11 eg6-letters/NIM/EG6_RTPC_NIM.tex
Reorganize for arxiv submission NIM and coherent

\begin{figure}[tbp]
\centering \includegraphics[scale=0.3]{fig/test_clas.png}
\caption{A three dimensional representation of the baseline CLAS setup. The
   full description is given in the text.} \label{fig:CLAS}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{fig_2017/RTPC_1_all.pdf}
\caption{Schematic drawing of the CLAS RTPC in a plane perpendicular to the beam 
direction. See text for description of the elements.} \label{fig:RTPC_1_4}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.70]{fig/GEM_photo.jpg}
\caption{Image of a typical GEM foil similar to the one used for our RTPC 
\cite{GEM_ref_pic}.} 
   \label{fig:GEMs}
\end{figure}

@@

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.55]{fig/PADs.png}
   \caption[]{A schematic representation of the readout pads. The 
   shaded sixteen pads are a group of pads that are connected to the same 
pre-amplifier.} \label{fig:PADs}
\end{figure}

@@

\begin{figure*}[tb]
   \centering
   \includegraphics[width=.75\textwidth]{fig/ReadoutScheme.png}
   \caption[]{Schematic representation of the RTPC readout system, showing
   the different elements of the front end electronics.} 
   \label{fig:ReadoutScheme}
\end{figure*}

@@

\begin{figure}[tb]
\centering
%\includegraphics[scale=0.4][trim={0 5cm 0 0},clip]{fig_2017/RTPC_1_4.pdf}
\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{fig_2017/RTPC_1_4.pdf}
\caption[]{A schematic drawing of a $^{4}$He track (in green) traversing the 
drift region, with the drift paths followed by the electrons (in black). } 
\label{fig:RTPC_signals}
\end{figure}

@@

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.42]{fig_2017/hits_time_profile.pdf}
   \caption[]{Time distribution of the hits associated with a track in one experimental run. Trigger
              time is defined as T=15, the time unit is the ALTRO sampling time of 100~ns.} 
   \label{fig:TDC_profile}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.42]{fig_2017/RunNumber_61452_TDCmax_Zslice.pdf}
\caption{Maximum time of collected hits as a function of the track
              position on the $z$-axis for one experimental run. } 
\label{fig:RunNumber_61551_TDCmax_Zslice}
\end{figure}

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=15.5cm]{fig_2017/Drift_run_number.pdf}
\caption{$T_{max/2}$ versus the experimental run numbers.} 
\label{fig:Drift_run_number_1}
\end{figure*}

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.42]{fig_2017/FitResult_p2_11.pdf}
\caption{$\Delta \phi$ versus T distribution for tracks
from one bin in longitudinal position along the RTPC. The black line represents 
the final drift paths in this bin.}
\label{fig:DELTA_PHI_TDC}
\end{figure}

@@

\begin{figure}[tb!]
   \centering
\includegraphics[scale=0.42]{fig_2017/Event_ADC_Graph_8799283.pdf}
\caption{Simulated (upper) and experimental (lower) ADC and T distributions 
of a track. The colors indicate the pads, same color in top and bottom indicate 
that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}

\begin{figure*}[tb]
\centering
\includegraphics[scale=0.73]{fig_2017/f_dedx_p_exp_2nd.pdf}
\caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distributions for the left (on the 
   left) and for the right (on the right) half of the RTPC after gain 
   calibration. The lines are theoretical expectations from the Bethe-Bloch 
   formula for $^4$He 
   (red), $^3$He (black), $^3$H (blue), $^2$H (pink) and protons (gray).}
\label{fig:dedx_p_exp_2nd}
\end{figure*}

@@

\begin{figure}[tb!]\centering
\includegraphics[scale=0.25]{fig/noisy_pad_before_rejection2.png}
\includegraphics[scale=0.25]{fig/noisy_pad_after_rejection2.png}
\caption{The ADC vs. T spectrum for an example noisy channel before (top) and 
after (bottom) noise rejection algorithms.  Only hits associated with tracks 
are included, and the selection of events and tracks is the same in both 
plots.}
\label{fig:noise}
\end{figure}

@@

\begin{figure}[tb]\centering
  \includegraphics[width=8cm]{fig/fit_W_distribution_l.png}
  \caption{The $W$ distribution calculated from electron kinematics before (``inclusive'')
  and after (``exclusive'') requiring a matching track in the RTPC.\label{fig:w}}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=8cm]{fig/tpceff.png}
\caption{The RTPC $^4$He detection efficiency as a function of the longitudinal 
   position along the detector.
 \label{fig:rtpc_eff}}
 \end{figure}

>>>>

\begin{figure}[tbp]
\centering \includegraphics[scale=0.3]{test_clas.png}
\caption{A three dimensional representation of the baseline CLAS setup. The
   full description is given in the text.} \label{fig:CLAS}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{RTPC_1_all.pdf}
\caption{Schematic drawing of the CLAS RTPC in a plane perpendicular to the beam 
direction. See text for description of the elements.} \label{fig:RTPC_1_4}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.70]{GEM_photo.jpg}
\caption{Image of a typical GEM foil similar to the one used for our RTPC 
\cite{GEM_ref_pic}.} 
   \label{fig:GEMs}
\end{figure}

@@

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.55]{PADs.png}
   \caption[]{A schematic representation of the readout pads. The 
   shaded sixteen pads are a group of pads that are connected to the same 
pre-amplifier.} \label{fig:PADs}
\end{figure}

@@

\begin{figure*}[tb]
   \centering
   \includegraphics[width=.75\textwidth]{ReadoutScheme.png}
   \caption[]{Schematic representation of the RTPC readout system, showing
   the different elements of the front end electronics.} 
   \label{fig:ReadoutScheme}
\end{figure*}

@@

\begin{figure}[tb]
\centering
\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{RTPC_1_4.pdf}
\caption[]{A schematic drawing of a $^{4}$He track (in green) traversing the 
drift region, with the drift paths followed by the electrons (in black). } 
\label{fig:RTPC_signals}
\end{figure}

@@

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.42]{hits_time_profile.pdf}
   \caption[]{Time distribution of the hits associated with a track in one experimental run. Trigger
              time is defined as T=15, the time unit is the ALTRO sampling time of 100~ns.} 
   \label{fig:TDC_profile}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.42]{RunNumber_61452_TDCmax_Zslice.pdf}
\caption{Maximum time of collected hits as a function of the track
              position on the $z$-axis for one experimental run. } 
\label{fig:RunNumber_61551_TDCmax_Zslice}
\end{figure}

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=15.5cm]{Drift_run_number.pdf}
\caption{$T_{max/2}$ versus the experimental run numbers.} 
\label{fig:Drift_run_number_1}
\end{figure*}

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.42]{FitResult_p2_11.pdf}
\caption{$\Delta \phi$ versus T distribution for tracks
from one bin in longitudinal position along the RTPC. The black line represents 
the final drift paths in this bin.}
\label{fig:DELTA_PHI_TDC}
\end{figure}

@@

\begin{figure}[tb!]
   \centering
\includegraphics[scale=0.42]{Event_ADC_Graph_8799283.pdf}
\caption{Simulated (upper) and experimental (lower) ADC and T distributions 
of a track. The colors indicate the pads, same color in top and bottom indicate 
that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}

\begin{figure*}[tb]
\centering
\includegraphics[scale=0.73]{f_dedx_p_exp_2nd.pdf}
\caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distributions for the left (on the 
   left) and for the right (on the right) half of the RTPC after gain 
   calibration. The lines are theoretical expectations from the Bethe-Bloch 
   formula for $^4$He 
   (red), $^3$He (black), $^3$H (blue), $^2$H (pink) and protons (gray).}
\label{fig:dedx_p_exp_2nd}
\end{figure*}

@@

\begin{figure}[tb!]\centering
\includegraphics[scale=0.25]{noisy_pad_before_rejection2.png}
\includegraphics[scale=0.25]{noisy_pad_after_rejection2.png}
\caption{The ADC vs. T spectrum for an example noisy channel before (top) and 
after (bottom) noise rejection algorithms.  Only hits associated with tracks 
are included, and the selection of events and tracks is the same in both 
plots.}
\label{fig:noise}
\end{figure}

@@

\begin{figure}[tb]\centering
  \includegraphics[width=8cm]{fit_W_distribution_l.png}
  \caption{The $W$ distribution calculated from electron kinematics before (``inclusive'')
  and after (``exclusive'') requiring a matching track in the RTPC.\label{fig:w}}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=8cm]{tpceff.png}
\caption{The RTPC $^4$He detection efficiency as a function of the longitudinal 
   position along the detector.
 \label{fig:rtpc_eff}}
 \end{figure}

### 2017-07-11 eg6-letters/coherent/dvcs_he4_prl.tex
Reorganize for arxiv submission NIM and coherent

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading-order handbag diagram of the DVCS 
process off $^4$He.}
\label{fig:diags}
\end{figure}

@@

\begin{figure}[tb]
\centering
\hspace{-0.45cm}
\includegraphics[width=9cm]{figs/F_all_coh_exc_cuts-pub.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the initial candidate events, while the shaded 
distributions represent those that passed all of the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied cuts.
The distributions from left to right and from top to bottom are: coplanarity 
angle $\Delta \phi$, missing energy $E_X$, missing-mass-squared $M_X^2$, and 
the cone angle $\theta$ between the measured photon and the missing momentum 
of the $e^\prime{^4}$He$^\prime$ system.}
\label{fig:kin-cuts}
\end{figure}

\begin{figure}[tb]
\hspace{-0.45cm}
\includegraphics[width=9cm]{figs/F_Q2_xB_t_Coh.pdf}
\caption{Coherent DVCS event distributions for $Q^2$ after exclusivity cuts. 
The distributions are shown as a function of Bjorken variable $x_B$ (left) 
and as a function of squared-momentum transfer $-t$ (right).}
\label{fig:kin-coverage}
\end{figure}

@@

\begin{figure}[tb]
   \centering
\includegraphics[width=8.5cm]{figs/F_Coherent_ALU_phi.pdf}
\caption{$A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
   bins (bottom panel).  The error bars represent the statistical 
   uncertainties. The grey bands represent the systematic uncertainties, 
   including the normalization uncertainties. The red curves are the results of 
   fits with Eq.~(\ref{eq:A_LU-coh}).}
\label{fig:alu}
\end{figure}

@@

\begin{figure*}[tb]
\includegraphics[width=16cm]{figs/F_Coherent_ALU_phi_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
   $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
   \cite{Airapetian}, and the curves are the theoretical calculations 
   from \cite{simonetta_2}. The grey bands represent the systematic errors.}
\label{fig:alu90}
\end{figure*}

\begin{figure}[tb]
\includegraphics[width=8.5cm]{figs/F_Coherent_CFF.pdf}
\caption{The leading-twist model-independent extraction of the imaginary (top panel) and
real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as a function of
$Q^{2}$ (left panel), $x_B$ (middle panel), and $t$ (right panel). The full red 
curves are the calculations based on the convolution model from Ref.~\cite{Vadim_priv}.
The black-dashed curves are calculations from the same 
model using different GPDs for the nucleons (VGG model~\cite{Guidal_priv}). The 
blue long-dashed curve on the top-right plot is from
the off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
\label{fig:CFF_HA}
\end{figure}

>>>>

\begin{figure}[tb]
\includegraphics[width=6.5cm]{DVCS_diagram.pdf}
\caption{Representation of the leading-order handbag diagram of the DVCS 
process off $^4$He.}
\label{fig:diags}
\end{figure}

@@

\begin{figure}[tb]
\centering
\hspace{-0.45cm}
\includegraphics[width=9cm]{F_all_coh_exc_cuts-pub.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the initial candidate events, while the shaded 
distributions represent those that passed all of the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied cuts.
The distributions from left to right and from top to bottom are: coplanarity 
angle $\Delta \phi$, missing energy $E_X$, missing-mass-squared $M_X^2$, and 
the cone angle $\theta$ between the measured photon and the missing momentum 
of the $e^\prime{^4}$He$^\prime$ system.}
\label{fig:kin-cuts}
\end{figure}

\begin{figure}[tb]
\hspace{-0.45cm}
\includegraphics[width=9cm]{F_Q2_xB_t_Coh.pdf}
\caption{Coherent DVCS event distributions for $Q^2$ after exclusivity cuts. 
The distributions are shown as a function of Bjorken variable $x_B$ (left) 
and as a function of squared-momentum transfer $-t$ (right).}
\label{fig:kin-coverage}
\end{figure}

@@

\begin{figure}[tb]
   \centering
\includegraphics[width=8.5cm]{F_Coherent_ALU_phi.pdf}
\caption{$A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
   bins (bottom panel).  The error bars represent the statistical 
   uncertainties. The grey bands represent the systematic uncertainties, 
   including the normalization uncertainties. The red curves are the results of 
   fits with Eq.~(\ref{eq:A_LU-coh}).}
\label{fig:alu}
\end{figure}

@@

\begin{figure*}[tb]
\includegraphics[width=16cm]{F_Coherent_ALU_phi_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
   $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
   \cite{Airapetian}, and the curves are the theoretical calculations 
   from \cite{simonetta_2}. The grey bands represent the systematic errors.}
\label{fig:alu90}
\end{figure*}

\begin{figure}[tb]
\includegraphics[width=8.5cm]{F_Coherent_CFF.pdf}
\caption{The leading-twist model-independent extraction of the imaginary (top panel) and
real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as a function of
$Q^{2}$ (left panel), $x_B$ (middle panel), and $t$ (right panel). The full red 
curves are the calculations based on the convolution model from Ref.~\cite{Vadim_priv}.
The black-dashed curves are calculations from the same 
model using different GPDs for the nucleons (VGG model~\cite{Guidal_priv}). The 
blue long-dashed curve on the top-right plot is from
the off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
\label{fig:CFF_HA}
\end{figure}
